TODO A Survey Paper

### 2015-12-07 FinalProject/Tex/paper/paper.tex
started outlining paper

\section{Architectural Overview}
\subsection{NVidia Warps}
TODO

\section{Challenges}
\subsection{Heterogeneous Applications}
TODO
\subsection{Memory Limitations}
TODO

\section{New Designs}
TODO

>>>>

\section{Architectural Overview}
\subsection{NVidia Warps}
TODO
Multiple threads are grouped together in "warps"
Thread within a warp are mapped to a vector functional unit (SIMD)
NVIDIA's Maxwell GPUs support up to 64 concurrent warps (2048 threads)
Talk about what a streaming multiprocessor is
Modern unified GPUs consist of multiple streaming multiprocessors (SMs)
  - warp (NVIDIA)/wavefronts (OpenCL)
  - similar to a SIMD processor
  - SM has a warp pool to store context of all running threads
  - HW warp scheduler dispatches and allocates resources
  - large (much larger than a CPU) register file shared across all threads
    - Maxwell architecture has 64K 32-bit registers for each SM
  - kernel: large number of threads executing same piece of code
  - multiple threads form a thread-block; same life-cycle, dispatched together
  - threads within a thread-block (32 or 64) organized into warps
  - warp scheduler schedules a ready warp each cycle, hiding latency of stalled warps
  - CPU launches GPU kernels by dispatching launch commands. Kernel parameters are passed from GPU to CPU at launch time and stored in GPU global memory
  - kernels from different streams are independent and can be run concurrently, but kernels within a stream are sequential
  - see DTBL paper for good intro
  - also see Locality Aware paper for internals of a SM
  - cooperative thread array (CTA) - see Weak behavior paper

\section{Challenges}
\subsection{Heterogeneous Applications}
TODO
Maximizing resource utilization while minimizing shared resource contention between CPU and GPU is hard
\subsection{Memory Limitations}
TODO

\section{New Designs}
Warp compression stuff
  Assist warps (CABA)
  Warped Compression
Dynamic tuning
  Coordinated warp scheduling (CAWA)
  Dynamic Thread Block Launch (DTBL)
  Equalizer
  Fine-grain Hardware Worklists (HWWL)
  Variable Warp Size (VWS)
CPU/GPU contention, NoC
  Managing Concurrency in Heterogeneous
Compiler/SW-only design
  Divergence Management
  Locality Aware Mapping
  (x) WeakBehaviorProgrammingAssumptions
